% RM_resume.tex

%---------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%---------------------------------------------------

\documentclass[11pt]{article}

\usepackage[left=0.75in,top=0.64in,right=0.75in,bottom=0.65in]{geometry} % Document margins
% \usepackage[margin=0.75in]{geometry}
\usepackage[parfill]{parskip}
\usepackage{fancyhdr, lastpage, array, ifthen, hyperref, multirow, xcolor}
\setlength{\headheight}{15.2pt}
\pagestyle{fancy}

% if want to change appearance of hyperlinks
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = {blue!75!black}, %Colour for external hyperlinks
  linkcolor    = black, %Colour of internal links
  % citecolor   = red %Colour of citations
}

%set footer info
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyhf[EOFR]{{\small Ryan Muraglia r\'esum\'e, Page \thepage ~of \pageref{LastPage} ; Last updated \today}}

% Defines the rSection environment for the large sections within the CV
\newenvironment{rSection}[1]{ % 1 input argument - section name
  \sectionskip
  \MakeUppercase{\bf #1} % Section title
  \sectionlineskip
  \hrule % Horizontal line
  \begin{list}{}{ % List for each individual item in the section
    \setlength{\leftmargin}{1.5em} % Margin within the section
  }
  \item[]
}{
  \end{list}
}

%Define rSubsection environment
\newenvironment{rSubsection}[4]{ % 4 input arguments - company name, year(s) employed, job title and location
 {\bf #1} \hfill {#2} % Bold company name and date on the right
 \ifthenelse{\equal{#3}{}}{}{ % If the third argument is not specified, don't print the job title and location line
  \\
  {\em #3} \hfill {\em #4} % Italic job title and location
  }
  \begin{list}{$\cdot$}{\leftmargin=0em} % \cdot used for bullets, no indentation
   \itemsep -0.5em \vspace{-0.5em} % Compress items in list together for aesthetics
  }{
  \end{list}
  \vspace{0.5em} % Some space after the list of bullet points
}

% The below commands define the whitespace after certain things in the document - they can be \smallskip, \medskip or \bigskip
\def\sectionlineskip{\smallskip} % The space above the horizontal line for each section 
\def\sectionskip{\smallskip} % The space after the heading section

%------------------------------------------------
%   DOCUMENT BEGINS HERE
%------------------------------------------------

\begin{document}

\begin{tabular}{ @{\hspace{1ex}} >{\bfseries}c @{\hspace{7ex}} >{\itshape}l @{\hspace{3ex}} l }
\multirow{4}{*}{{\Huge Ryan Muraglia}} 
  & Address & 1209 E Florida Ave, Apt 33A, Urbana, IL 61801 \\
  & Phone & (310) 940 8613 \\
  & Email & \href{mailto:rmuraglia@gmail.com}{rmuraglia@gmail.com} \\
  & Website & \url{https://github.com/rmuraglia}
\end{tabular} 

%-------------------------------------------------
% SKILLS
%-------------------------------------------------

\begin{rSection}{Summary}
Motivated \& detail-oriented recent graduate trained in computer science, statistics \& biology. 
Passion for data-driven decision making \& effective communication through elegant visualization.
Excellent ability to work \& learn independently, with strong interpersonal skills to flourish in team-based environments. 
Experienced with various classification, regression \& clustering techniques in R \& Python.
\end{rSection}

%------------------------------------------
%   EDUCATION
%------------------------------------------

\begin{rSection}{Education}

{\bf Duke University}, Durham, NC \hfill August 2012 - August 2016 \\
M.S., Computational Biology \& Bioinformatics (CBB) \hfill GPA: 3.7/4.0 \\
{\em {\small (Former Ph.D candidate (ABD). Student-initiated voluntary withdrawal - preliminary exam completed 02/2015)}}
\begin{list}{$\cdot$}{\leftmargin=1.5em} % \cdot used for bullets, no indentation
   \itemsep -0.5em \vspace{-0.5em} % Compress items in list together for aesthetics
   \item \underline{Thesis}: \href{https://dl.dropboxusercontent.com/u/42186570/RM_thesis.pdf}{``Path optimization in free energy calculations''} {\small w/ Scott Schmidler, Dept. of Statistical Science} \\ 
   Used reinforcement learning techniques (Q-learning, multi-armed bandit), dynamic programming graph search algorithms and sequential Monte Carlo sampling to achieve 2-5X reduction in computational cost of estimating free energies of binding for trial mutations in rational molecular design. % add hyperlinks for images in here as well?
   \item \underline{Honors \& Awards}: Chancellor's scholarship (2012, \$5,000), Best poster (CBB departmental retreat 2014, \$100), Selected student research presentation (CBB recruitment 2016)
   \item \underline{Teaching \& Leadership}: CBB student committee chair, CBB 540 TA, CBB 511 discussion leader
\end{list}

\vspace{-0.0ex}
{\bf University of Michigan}, Ann Arbor, MI \hfill September 2007 - April 2011 \\ 
B.S., Microbiology; Academic Minor, Physics \hfill GPA: 3.6/4.0
\begin{list}{$\cdot$}{\leftmargin=1.5em} 
   \itemsep -0.5em \vspace{-0.5em} 
   \item \underline{Research}: Analyzed high throughput 454 pyrosequencing data of gut microbiome in R.
   \item \underline{Honors \& Awards}: University honors (2009 - 2011), James B. Angell Scholar (2011)
\end{list}

\vspace{-0.0ex}
{\bf Selected Coursework}\\
\begin{list}{$\cdot$}{\leftmargin=0em} 
   \itemsep -0.5em \vspace{-2.0em} 
   \item STA 863 Advanced statistical computing (Duke): MCMC methods, convergence \& convex optimization % gibbs sampling, hybrid monte carlo, tempering, inference (kalman filter)
   \item CMPLXSYS 430 Math. modeling of infectious diseases (UM): ODE methods \& inference in MATLAB
   \item CBB 540 Statistical methods in computational biology (Duke): Regression, EM \& HMMs in R
   \item COMPSCI 270 Introduction to AI (Duke): Markov decision processes \& machine learning in Python
   \item Coursera: {\small Machine learning (Stanford), Using databases w/ Python (UM), Getting \& cleaning data (JHU)}
\end{list}
\end{rSection}

%-------------------------------------------------
% SKILLS
%-------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} l }
Scientific Computing & Proficient in R and Python. Comfortable with MATLAB/Octave \\ % remove octave and put in scipy stack?
Cluster Computing & Unix, shell scripting, experienced in use of SLURM and SGE schedulers \\
% Statistical techniques?
Data Handling & MySQL, SQLite, dplyr, tidyr, retrieving JSON and XML from APIs \\ % add pandas?
Presentation & \LaTeX, beamer, ggplot2, knitr, Jupyter, Microsoft Powerpoint \\
% Languages & English (native), French (fluent), Spanish (conversational) \\
Miscellaneous & Git, Microsoft Office (Word, Excel), Windows, Mac and Linux OS
\end{tabular}

\end{rSection}

%-------------------------------------------------
% NON-ACADEMIC PROJECTS
%-------------------------------------------------

\begin{rSection}{Non-academic projects}

\textbf{Analysis and visualization of Smash 4 data} \hfill \textit{Primary tools: R, ggplot2, MySQL} \\
\begin{list}{$\cdot$}{\leftmargin=0em} 
   \itemsep -0.5em \vspace{-2.0em} 
   \item A statistical perspective on character balance and strength in fighting games. Data represent character attributes and match records from a matchmaking website ($\sim$50K games/week, $\sim$2M total in DB).
   \item Analyses are varied, and range from \href{https://dl.dropboxusercontent.com/u/42186570/char_co-usage_icons.png}{heat maps} for character co-usage rates, to \href{https://dl.dropboxusercontent.com/u/42186570/4BR_v_runspeed_nozoom.png}{models} using character attributes as predictors of performance, to \href{https://dl.dropboxusercontent.com/u/42186570/4br-1.1.6-sorted-deltas.png}{revisualizations} highlighting trends in community opinion.
   % \item Information disseminated, 10K impressions, 1.5K media engagements for each viz
\end{list}

\vspace{-0.2ex}
\textbf{Development of the NC Smash 4 player database} \hfill \textit{Primary tools: MySQL, Python} \\
\begin{list}{$\cdot$}{\leftmargin=0em} 
   \itemsep -0.5em \vspace{-2.0em} 
   \item Created database to facilitate tournament organization and improve seeding accuracy by tracking player performance ($\sim$40-60 unique entrants at local weeklies, $\sim$200 at regional). % add number in db
   \item Past tournament results are programmatically inserted into a MySQL DB using the challonge.com API.
\end{list}

\end{rSection}

\end{document}
